Transient Variability In Vapor Intrusion And The Factors That Influence It

### 2019-03-13 tex/main.tex
Writing

The modeled surrounding soil domain extends 5 meters from the perimeter of the house, and is assumed to consist of sandy clay (except as noted).
Directly beneath the foundation slab, there is assumed to be a 30 cm (one foot) thick gravel layer, except in certain cases where this sub-base material is assumed to be the same as the surrounding soil (termed  a ”uniform” soil scenario). \par

@@

    % Sand
    Sand     & $9.9 \cdot 10^{-12}$  & 1430    & 0.38        & 0.053        & 3.5       & 3.2 \\
    % Sandy clay
    Sandy Clay    & $1.7 \cdot 10^{-14}$  & 1470    & 0.39        & 0.12        & 3.3       & 1.2 \\

@@

@@

To examine the role that $p_\mathrm{in/out}$ and $A_e$ play in determining $c_\mathrm{in}$ variability (given as attenuation from groundwater vapor source $\alpha_\mathrm{gw}$ here), we first consider modeling VI scenarios with a constant $A_e = 0.5 \; \mathrm{(1/hr)}$ (the mean $A_e$ at the ASU house), and varying $p_\mathrm{in/out}$ from 5 to -5 Pa.
The first of these scenarios is aimed to be similar to the period when the preferential pathway is open at the ASU house, and thus the modeled preferential pathway is active.
In the second scenario, this preferential pathway feature is deactivated, akin to the period when the preferential pathway was closed at the ASU site.
And in the third, the preferential pathway is again modeled, but the permeable gravel sub-base is instead assumed consist of the sandy loam, just like the surrounding soil, giving an "uniform soil" scenario. % TODO: Make sure that the soil type is correct
The results of these modeled scearios are then compared to the preferential pathways "open" and "closed" periods from the ASU data, and may be seen in Figure \ref{fig:land_drain_scenarios_constant_ae}.
The data is here binned into evenly spaced bins, with each dot representing the mean $\alpha_\mathrm{gw}$ and the error bars denote the one standard deviation.

>>>>

The modeled surrounding soil domain extends 5 meters from the perimeter of the house, and is assumed to consist of sandy loam (except as noted).
Directly beneath the foundation slab, there is assumed to be a 30 cm (one foot) thick gravel layer, except in certain cases where this sub-base material is assumed to be the same as the surrounding soil (termed  a ”uniform” soil scenario). \par

@@

    % sandy loam
    Sandy Loam    & $5.9 \cdot 10^{-13}$  & 1460    & 0.39        & 0.039        & 2.7       & 1.4 \\

@@

\subsection{Variability Of Attenuation From Subslab}

\begin{figure}[htb!]
  \caption{Boxplot of attenuation from subslab at the ASU house site. The box shows the quartiles of the distribution, the whiskers the extent of the distribution, and diamonds are points that are considered outlier.}\label{fig:attenuation_subslab}
  \includegraphics[width=0.7\textwidth]{asu_attenuation_subslab.pdf}
\end{figure}

To examine how $p_\mathrm{in/out}$ affects the contaminant entry rate it would be most convenient to analyze how $p_\mathrm{in/out}$ is correlated with the attenuation from subslab ($\alpha_\mathrm{subslab} = c_\mathrm{in}/c_\mathrm{subslab}$) at a site - in particularly for understanding how the PP at the ASU house affected the site dynamics.
By normalizing the $c_\mathrm{in}$ to $c_\mathrm{subslab}$ the $p_\mathrm{in/out}$ influence on the contaminant availability in the subslab area is mitigated.
The $c_\mathrm{subslab}$ are taken from the soilgas probe labeled as "6" at the ASU house, which is the probe located closest to the preferential pathway, and to a reported breach in the foundation\cite{guo_identification_2015}.
However, as Figure \ref{fig:attenuation_subslab} shows, there are some issues with doing so.

First, we can state that during the period when the preferential pathway was closed, $\alpha_\mathrm{subslab}$ does not vary that significantly, and is mostly around the EPA recommended $\alpha_\mathrm{subslab}$ value of 0.03. % TODO: Reference the EPA report that recommends this
During the period when the preferential pathway was open, there is considerably more variability, and it is not uncommon for the $\alpha_\mathrm{subslab}$ to exceed unity.

Even though probe "6" is located in such close proximity to the preferential pathway, and the breach in the foundation, the contaminant concentration 'hotspot' is still missed.
This suggests that a preferential pathway may have an extremely localized influence in the subslab region, causing significant spatial variability in $c_\mathrm{subslab}$.
This shows how difficult it may be to locate a preferential pathway through subslab soilgas sampling.

The large $\alpha_\mathrm{subslab}$ values (compared to the recommended EPA value of 0.03) can often indicate that there may be indoor sources present a site, which there were none of at the ASU house.
Thus, in addition to potentially indicating indoor contaminant sources, large $\alpha_\mathrm{subslab}$ may also indicate the presence of a preferential pathway.

@@

\begin{figure}[htb!]
	\centering
  \caption{Simulated cases}
  \label{fig:land_drain_scenarios}
  \includegraphics[width=\textwidth]{land_drain_scenarios_combo.pdf}
\end{figure}

To examine the role that $p_\mathrm{in/out}$ play in determining $c_\mathrm{in}$ variability (given as attenuation from groundwater vapor source $\alpha_\mathrm{gw}$ here), we first consider modeling VI scenarios with a constant $A_e = 0.5 \; \mathrm{(1/hr)}$ (the mean $A_e$ at the ASU house), and varying $p_\mathrm{in/out}$ from 5 to -5 Pa.
The first of these scenarios is aimed to be similar to the period when the preferential pathway is open at the ASU house, and thus the modeled preferential pathway is active.
In the second scenario, this preferential pathway feature is deactivated, akin to the period when the preferential pathway was closed at the ASU site.
And in the third, the preferential pathway is again modeled, but the permeable gravel sub-base is instead assumed consist of the sandy loam, just like the surrounding soil, giving an "uniform soil" scenario. % TODO: Make sure that the soil type is correct
The results of these modeled scearios are then compared to the preferential pathways "open" and "closed" periods from the ASU data, and may be seen in Figure \ref{fig:land_drain_scenarios_constant_ae}.
The data is here binned into evenly spaced bins, with each dot representing the mean $\alpha_\mathrm{gw}$ and the error bars denote the one standard deviation.
